---
title: "Full-Span BrainAge models - Clean Code"
author: "SYC"
date: "2026-05-02"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(randomForest)
library(partykit)
library(vip)
library(pdp)
library(tibble)
library(longCombat)
library(janitor)
library(gbm)
library(gpboost)
library(SHAPforxgboost)
library(corrplot)
library(readxl)
library(tidyr)
library(purrr)
library(ggplot2)
library(stringr)
library(dplyr)
```

## Load data
### Neuroimaging Input Features and Demographics
```{r}

df.har <- read.csv("/data/dfe_har.csv")

demo_cov <- read.csv("/data/dfe_cov.csv")

```


## GPBOOST PREP
```{r}

dff <- transform(df.har, id = as.numeric(factor(subjid)))

id.key <- dff %>%
  select(subjid, id) %>%
  unique()

test <- dff %>%
  filter(is.na(ScanAge))

test_dat <- dff %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, sex, time, batch, ds)

```

## Stratify by Sex
```{r}

dff.m <- dff %>%
  filter(sex == "Male") %>%
  arrange(subjid, ScanAge)

test_dat.m <- dff.m %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train.m <- dff.m %>%
  filter(is.na(test))

dff.f <- dff %>%
  filter(sex == "Female") %>%
  arrange(subjid, ScanAge)

test_dat.f <- dff.f %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train.f <- dff.f %>%
  filter(is.na(test))

```

Create Folds for internal validation
**FOLDS REPEATED - Males**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

rand.seed <- sample(1:1000,10)
folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:720, 720) 

  k.folds <- groupKFold(group = train.m[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.m <- flatten(folds.out)

```

**FOLDS REPEATED - Females**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:784, 784) 

  k.folds <- groupKFold(group = train.f[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.f <- flatten(folds.out)

```

```{r}

# Specify parameter grid, gp_model, and gpb.Dataset
param_grid <- list("learning_rate" = c(1,0.1,0.01), "max_depth" = c(1,2,3,5,10,15),"min_data_in_leaf" = c(5,10,50,100), "lambda_l2" = c(0,1,10,25,50))
other_params <- list(num_leaves = 2^10)


```


## S1 Freesurfer Thickness Alone
### Males
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.1, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 25)
nrounds <- 371
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.m <- gpb.out
mod.s1.m <- shap.plot.summary.wrap1(s1.out.m, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.m 

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_s1m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 0)
nrounds <- 1812
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.f <- gpb.out
mod.s1.f <- shap.plot.summary.wrap1(s1.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.f 

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_s1f <- pred[["response_mean"]]

```

## S2 Freesurfer Thickness + Subcort
### Males
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.1, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 10)
nrounds <- 308
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.m <- gpb.out
mod.s2.m <- shap.plot.summary.wrap1(s2.out.m, X = data_train[,pred_vars], top_n=20) +  ggtitle("SHAP values")

mod.s2.m 

```

### Predict Age in Test 
```{r}

pred <- predict(s2.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_s2m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 1)
nrounds <- 182
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.f <- gpb.out
mod.s2.f <- shap.plot.summary.wrap1(s2.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s2.f 

```

### Predict Age in Test 
```{r}

pred <- predict(s2.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_s2f <- pred[["response_mean"]]

```

## F1 Functional Measures
### Males
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 370
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

f1.out.m <- gpb.out
mod.f1.m <- shap.plot.summary.wrap1(f1.out.m, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.m

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_f1m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 0)
nrounds <- 1355
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

f1.out.f <- gpb.out
mod.f1.f <- shap.plot.summary.wrap1(f1.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.f

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_f1f <- pred[["response_mean"]]

```

## A1 Freesurfer Thickness + Subcort + 17 FC recruitment
### Males
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.1, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 10)
nrounds <- 299
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 2)
summary(gp_model)

```

### SHAP
```{r}

a1.out.m <- gpb.out
mod.a1.m <- shap.plot.summary.wrap1(a1.out.m, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.m

```

### Predict Age in Test 
```{r}

pred <- predict(a1.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_a1m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 25)
nrounds <- 1975
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)

summary(gp_model)

```
### SHAP
```{r}

a1.out.f <- gpb.out
mod.a1.f <- shap.plot.summary.wrap1(a1.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.f

```

### Predict Age in Test 
```{r}

pred <- predict(al.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_a1f <- pred[["response_mean"]]

```


## A2 Freesurfer Thickness + Subcort + 17 FC Integration
### Males
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 1, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 702
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a2.out.m <- gpb.out
mod.a2.m <- shap.plot.summary.wrap1(a2.out.m, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.m

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_a2m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 1)
nrounds <- 1331
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```
### SHAP
```{r}

a2.out.f <- gpb.out
mod.a2.f <- shap.plot.summary.wrap1(a2.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.f

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_a2f <- pred[["response_mean"]]

```

## A3 Freesurfer Thickness + Subcort + 17 FC integration + Rec
### Males 
```{r}
# convert data into matrix

data_train <- dff.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 1, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 705
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.m <- gpb.out
mod.a3.m <- shap.plot.summary.wrap1(a3.out.m, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.m

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.m, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.m$gpb_pred_a3m <- pred[["response_mean"]]

```

### Females
```{r}
# convert data into matrix

data_train <- dff.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 1)
nrounds <- 1321
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.f <- gpb.out
mod.a3.f <- shap.plot.summary.wrap1(a3.out.f, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.f

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.f, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat.f$gpb_pred_a3f <- pred[["response_mean"]]

```


### Write Test Data
```{r}

write.csv(test_dat.f, '/output/brainage_f.csv', row.names = FALSE)

write.csv(test_dat.m, '/output/brainage_m.csv', row.names = FALSE)

```
