---
title: "Phase-Specific BrainAge models - Clean Code"
author: "SYC"
date: "2026-05-02"
output: html_document
---

```{r setup, include=FALSE}
library(caret)
library(randomForest)
library(partykit)
library(vip)
library(pdp)
library(tibble)
library(longCombat)
library(janitor)
library(gbm)
library(gpboost)
library(SHAPforxgboost)
library(corrplot)
library(readxl)
library(tidyr)
library(purrr)
library(ggplot2)
library(stringr)
library(dplyr)
```


## Load data
### Neuroimaging Input Features and Demographics
```{r}

df.har <- read.csv("/data/dfe_har.csv")

demo_cov <- read.csv("/data/dfe_cov.csv")

```

## GPBOOST PREP
```{r}

dff <- transform(df.har, id = as.numeric(factor(subjid)))

id.key <- dff %>%
  select(subjid, id) %>%
  unique()

test <- dff %>%
  filter(is.na(ScanAge))

test_dat <- dff %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, sex, time, batch, ds)

train.id <- dff %>%
  filter(is.na(test)) %>%
  select(subjid, ds, sex) %>%
  unique(.)

test.id <- test_dat %>%
  select(subjid, ds, sex) %>%
  unique(.)
  

```

## Stratify by Phase 
```{r}

dff1 <- dff %>%
  filter(time < 4 | time == 6)

dff2 <- dff %>%
  filter(time >=3 & time < 6)

fivenum(dff1$ScanAge)
fivenum(dff2$ScanAge)

```

## Stratify by Sex
### Phase 1 (up to 8YO)
```{r}

dff1.m <- dff1 %>%
  filter(sex == "Male") %>%
  arrange(subjid, ScanAge)

test_dat1.m <- dff1.m %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train1.m <- dff1.m %>%
  filter(is.na(test))

dff1.f <- dff1 %>%
  filter(sex == "Female") %>%
  arrange(subjid, ScanAge)

test_dat1.f <- dff1.f %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train1.f <- dff1.f %>%
  filter(is.na(test))

```

### Phase 2 (up to 7 to 13YO)
```{r}

dff2.m <- dff2 %>%
  filter(sex == "Male") %>%
  arrange(subjid, ScanAge)

test_dat2.m <- dff2.m %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train2.m <- dff2.m %>%
  filter(is.na(test))

dff2.f <- dff2 %>%
  filter(sex == "Female") %>%
  arrange(subjid, ScanAge)

test_dat2.f <- dff2.f %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train2.f <- dff2.f %>%
  filter(is.na(test))

```

Create Folds for internal validation (5-folds Repeated 5 times)
**FOLDS REPEATED - Males Phase 1**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

rand.seed <- sample(1:1000,10)
folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:422, 422) 

  k.folds <- groupKFold(group = train1.m[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.m1 <- flatten(folds.out)

```

**FOLDS REPEATED - Males Phase 2**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:487, 487) 

  k.folds <- groupKFold(group = train2.m[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.m2 <- flatten(folds.out)

```

**FOLDS REPEATED - Females Phase 1**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:459, 459) 

  k.folds <- groupKFold(group = train1.f[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.f1 <- flatten(folds.out)

```

**FOLDS REPEATED - Females Phase 2**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:519, 519) 

  k.folds <- groupKFold(group = train2.f[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.f2 <- flatten(folds.out)

```

```{r}

# Specify parameter grid, gp_model, and gpb.Dataset
param_grid <- list("learning_rate" = c(1,0.1,0.01), "max_depth" = c(1,2,3,5,10,15),"min_data_in_leaf" = c(5,10,50,100), "lambda_l2" = c(0,1,10,25,50))
other_params <- list(num_leaves = 2^10)


```

## S1 Freesurfer Thickness Alone
Tree Boosting with Random Effects \
https://github.com/fabsig/GPBoost \

### Males 1 
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 364
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.m1 <- gpb.out
mod.s1.m1 <- shap.plot.summary.wrap1(s1.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.m1

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_s1 <- pred[["response_mean"]]

```

### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 1086
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.m2 <- gpb.out
mod.s1.m2 <- shap.plot.summary.wrap1(s1.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.m2

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_s1 <- pred[["response_mean"]]


```

### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 1, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 0)
nrounds <- 237
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.f1 <- gpb.out
mod.s1.f1 <- shap.plot.summary.wrap1(s1.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.f1

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_s1 <- pred[["response_mean"]]

```

### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:70]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 10, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 25)
nrounds <- 130
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s1.out.f2 <- gpb.out
mod.s1.f2 <- shap.plot.summary.wrap1(s1.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s1.f2

```

### Predict Age in Test 
```{r}


pred <- predict(s1.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_s1 <- pred[["response_mean"]]


```


## S2 Freesurfer Thickness + Subcort
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.1, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 52
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.m1 <- gpb.out
mod.s2.m1 <- shap.plot.summary.wrap1(s2.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s2.m1

```

### Predict Age in Test 
```{r}

pred <- predict(s2.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_s2 <- pred[["response_mean"]]

```

### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()


data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 1689
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.m2 <- gpb.out
mod.s2.m2 <- shap.plot.summary.wrap1(s2.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s2.m2

```

### Predict Age in Test 
```{r}

pred <- predict(s2.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_s2 <- pred[["response_mean"]]

```

### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 343
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.f1 <- gpb.out
mod.s2.f1 <- shap.plot.summary.wrap1(s2.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s2.f1

```

### Predict Age in Test 
```{r}


pred <- predict(s2.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_s2 <- pred[["response_mean"]]

```

### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right")) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:84]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 846
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

s2.out.f2 <- gpb.out
mod.s2.f2 <- shap.plot.summary.wrap1(s2.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.s2.f2

```

### Predict Age in Test 
```{r}

pred <- predict(s2.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_s2 <- pred[["response_mean"]]

```

## F1 Functional Measures
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 172
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

f1.out.m1 <- gpb.out
mod.f1.m1 <- shap.plot.summary.wrap1(f1.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.m1

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_f1 <- pred[["response_mean"]]

```


### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 159
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

f1.out.m2 <- gpb.out
mod.f1.m2 <- shap.plot.summary.wrap1(f1.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.m2

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_f1 <- pred[["response_mean"]]

```


### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.01, max_depth = 15, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 10)
nrounds <- 135
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

f1.out.f1 <- gpb.out
mod.f1.f1 <- shap.plot.summary.wrap1(f1.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.f1

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_f1 <- pred[["response_mean"]]

```

### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:156]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 50)
nrounds <- 347
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```
### SHAP
```{r}

f1.out.f2 <- gpb.out
mod.f1.f2 <- shap.plot.summary.wrap1(f1.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.f1.f2

```

### Predict Age in Test 
```{r}

pred <- predict(f1.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_f1 <- pred[["response_mean"]]

```

## A1 Freesurfer Thickness + Subcort + 17 FC recruitment
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 546
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a1.out.m1 <- gpb.out
mod.a1.m1 <- shap.plot.summary.wrap1(a1.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.m1

```

### Predict Age in Test 
```{r}

pred <- predict(a1.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_a1 <- pred[["response_mean"]]

```

### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()


data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 25)
nrounds <- 822
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a1.out.m2 <- gpb.out
mod.a1.m2 <- shap.plot.summary.wrap1(a1.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.m2

```

### Predict Age in Test 
```{r}

pred <- predict(a1.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_a1 <- pred[["response_mean"]]

```


### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 331
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)

summary(gp_model)

```

### SHAP
```{r}

a1.out.f1 <- gpb.out
mod.a1.f1 <- shap.plot.summary.wrap1(a1.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.f1

```

### Predict Age in Test 
```{r}

pred <- predict(a1.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_a1 <- pred[["response_mean"]]

```


### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:102]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 811
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a1.out.f2 <- gpb.out
mod.a1.f2 <- shap.plot.summary.wrap1(a1.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a1.f2

```

### Predict Age in Test 
```{r}

pred <- predict(a1.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_a1 <- pred[["response_mean"]]

```


## A2 Freesurfer Thickness + Subcort + 17 FC Integration
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 1)
nrounds <- 301
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.m1 <- gpb.out
mod.a2.m1 <- shap.plot.summary.wrap1(a2.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.m1

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_a2 <- pred[["response_mean"]]

```


### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()


data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 10)
nrounds <- 1029
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.m2 <- gpb.out
mod.a2.m2 <- shap.plot.summary.wrap1(a2.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.m2

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_a2 <- pred[["response_mean"]]

hist(test_dat2.m$ScanAge)
hist(test_dat2.m$gpb_pred_a2)

cor.test(test_dat2.m$ScanAge, test_dat2.m$gpb_pred_a2)

test.gpb <- test_dat2.m %>%
  select(subjid, time, ScanAge, gpb_pred_a2) %>%
  mutate(gpb_pad = gpb_pred_a2 - ScanAge) %>% 
  mutate(gpb_mae = abs(ScanAge-gpb_pred_a2)) 

round(mean(test.gpb$gpb_mae),3)
round(sd(test.gpb$gpb_mae),3)

```


### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 652
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.f1 <- gpb.out
mod.a2.f1 <- shap.plot.summary.wrap1(a2.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.f1

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_a2 <- pred[["response_mean"]]

```


### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 0)
nrounds <- 916
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.f2 <- gpb.out
mod.a2.f2 <- shap.plot.summary.wrap1(a2.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.f2

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_a2 <- pred[["response_mean"]]

```

## A3 Freesurfer Thickness + Subcort + 17 FC integration + Rec
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 289
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.m1 <- gpb.out
mod.a3.m1 <- shap.plot.summary.wrap1(a3.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.m1

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_a3 <- pred[["response_mean"]]

```


### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 10)
nrounds <- 1014
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.m2 <- gpb.out
mod.a3.m2 <- shap.plot.summary.wrap1(a3.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.m2

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_a3 <- pred[["response_mean"]]

```

### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```


```{r}

params <- list(learning_rate = 0.01, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 0)
nrounds <- 642
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.f1 <- gpb.out
mod.a3.f1 <- shap.plot.summary.wrap1(a3.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.f1

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_a3 <- pred[["response_mean"]]

```

### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("Left|Right"), starts_with("Int"), starts_with("Rec."), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:238]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 5, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 50)
nrounds <- 747
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
```{r}

a3.out.f2 <- gpb.out
mod.a3.f2 <- shap.plot.summary.wrap1(a3.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a3.f2

```

### Predict Age in Test 
```{r}

pred <- predict(a3.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_a3 <- pred[["response_mean"]]

```

## Write Test Data
```{r}

test_dat1.f <- test_dat1.f %>%
  mutate(sex = "Female") %>%
  mutate(phase = "Early-Childhood")

test_dat2.f <- test_dat2.f %>%
  mutate(sex = "Female") %>%
  mutate(phase = "Late-Childhood")

test_dat1.m <- test_dat1.m %>%
  mutate(sex = "Male") %>%
  mutate(phase = "Early-Childhood")

test_dat2.m <- test_dat2.m %>%
  mutate(sex = "Male") %>%
  mutate(phase = "Late-Childhood")

write.csv(test_dat1.f, '/output/brainage_sep_f1.csv', row.names = FALSE)

write.csv(test_dat2.f, '/output/brainage_sep_f2.csv', row.names = FALSE)

write.csv(test_dat1.m, '/output/brainage_sep_m1.csv', row.names = FALSE)

write.csv(test_dat2.m, '/output/brainage_sep_m2.csv', row.names = FALSE)

```

## Selected A2 Model
### Save models gpboost
```{r}

setwd('/output/models')

saveRDS(pred_vars, "a2_pred_vars.rds")

gpb.save(a2.out.m1, "a2_m1_phase.json")
saveRDS.gpb.Booster(a2.out.m1, "a2_m1_phase.rds")

gpb.save(a2.out.m2, "a2_m2_phase.json")
saveRDS.gpb.Booster(a2.out.m2, "a2_m2_phase.rds")

gpb.save(a2.out.f1, "a2_f1_phase.json")
saveRDS.gpb.Booster(a2.out.f1, "a2_f1_phase.rds")

gpb.save(a2.out.f2, "a2_f2_phase.json")
saveRDS.gpb.Booster(a2.out.f2, "a2_f2_phase.rds")

```

### SHAP values
### Males Phase 1
#### Values Train
```{r}
shap.a2.m1 <- shap.values(a2.out.m1, X_train = data_train[,pred_vars])
shap.a2.m1 <- as.data.frame(shap.a2.m1$mean_shap_score)
shap.a2.m1 <- shap.a2.m1 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m1$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m1, '/output/shap.a2.m1.csv')

```

#### Values Test
```{r}
shap.a2.m1_test <- shap.values(a2.out.m1, X_train = data_test[,pred_vars])
shap.a2.m1_test <- as.data.frame(shap.a2.m1_test$mean_shap_score)
shap.a2.m1_test <- shap.a2.m1_test %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m1_test$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m1_test, '/output/shap.a2.m1_test.csv')

```

### Males Phase 2
#### Values Train
```{r}

shap.a2.m2 <- shap.values(a2.out.m2, X_train = data_train[,pred_vars])
shap.a2.m2 <- as.data.frame(shap.a2.m2$mean_shap_score)
shap.a2.m2 <- shap.a2.m2 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m2$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m2, '/output/shap.a2.m2.csv')

```

#### Values Test
```{r}
shap.a2.m2_test <- shap.values(a2.out.m2, X_train = data_test[,pred_vars])
shap.a2.m2_test <- as.data.frame(shap.a2.m2_test$mean_shap_score)
shap.a2.m2_test <- shap.a2.m2_test %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m2_test$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m2_test, '/output/shap.a2.m2_test.csv')

```

Females Phase 1
#### Values Train
```{r}

shap.a2.f1 <- shap.values(a2.out.f1, X_train = data_train[,pred_vars])
shap.a2.f1 <- as.data.frame(shap.a2.f1$mean_shap_score)
shap.a2.f1 <- shap.a2.f1 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f1$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f1, '/output/shap.a2.f1.csv')

```

#### Values Test
```{r}

shap.a2.f1_test <- shap.values(a2.out.f1, X_train = data_test[,pred_vars])
shap.a2.f1_test <- as.data.frame(shap.a2.f1_test$mean_shap_score)
shap.a2.f1_test <- shap.a2.f1_test %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f1_test$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f1_test, '/output/shap.a2.f1_test.csv')

```

### Females Phase 2
#### Values Train
```{r}

shap.a2.f2 <- shap.values(a2.out.f2, X_train = data_train[,pred_vars])
shap.a2.f2 <- as.data.frame(shap.a2.f2$mean_shap_score)
shap.a2.f2 <- shap.a2.f2 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f2$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f2, '/output/shap.a2.f2.csv')

```

#### Values Test
```{r}

shap.a2.f2_test <- shap.values(a2.out.f2, X_train = data_test[,pred_vars])
shap.a2.f2_test <- as.data.frame(shap.a2.f2_test$mean_shap_score)
shap.a2.f2_test <- shap.a2.f2_test %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f2_test$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f2_test, '/output/shap.a2.f2_test.csv')

```
