---
title: "Results One - Candidate Models Comparisons clean"
author: "SYC"
date: "2026-05-02"
output: html_document
---

## Packages
```{r}

library(flextable)
library(officer)
library(tidyr)
library(dplyr)
library(gt)
library(corx)
library(rmarkdown)
library(broom)
library(stringr)
library(forestplot)
library(purrr)
library(moments)
library(readr)

```

## Candidate BrainAge Models
### Sex-specific only (Full-Span Models)
```{r}

df.m <- read.csv('/output/brainage_m.csv')

rename.cols <- colnames(df.m)[7:12]
rename.cols <- substr(rename.cols, start = 1, stop = 11)
rename.cols <- paste(rename.cols, "sex", sep="_")

df.m2 <- df.m %>%
  mutate(sex = "Male")

colnames(df.m2)[7:12] <- rename.cols 

df.f <- read.csv('/output/brainage_f.csv')

df.f2 <- df.f %>%
  mutate(sex = "Female")

colnames(df.f2)[7:12] <- rename.cols 

df.all_sex <- rbind(df.f2, df.m2)

rm(df.m, df.f)

```

### Sex and Phase specific 
```{r}

df.m1 <- read.csv('/output/brainage_sep_m1.csv')

df.m2 <- read.csv('/output/brainage_sep_m2.csv')

df.f1 <- read.csv('/output/brainage_sep_f1.csv')

df.f2 <- read.csv('/output/brainage_sep_f2.csv')

df.all <- rbind(df.m1, df.m2, df.f1, df.f2)

colnames(df.all)[7:12] <- paste(colnames(df.all)[7:12], "phase", sep="_")

df.all_phase <- df.all

rm(df.m1, df.m2, df.f1, df.f2, df.all)

```

### Merge
```{r}

df.all <- merge(df.all_sex, df.all_phase, by = c("subjid", "id", "ScanAge", "time", "batch", "ds", "sex"), sort = FALSE)

```

## Table 1: Model Metrics
**Table 1A and Table 1B**
```{r}

own.ba.sum <- df.all %>%
  gather(key = "model", value = "BrainAge", -subjid, -id, -ScanAge, -time, -batch, -ds, -sex, -phase) %>%
  mutate(BrainPAD = BrainAge - ScanAge) %>%
  mutate(AE = abs(ScanAge - BrainAge))

sumtable1 <- own.ba.sum %>%
  group_by(model, sex, phase) %>%
  summarise(across(c(BrainAge, BrainPAD, AE), list(
    mean = ~mean(., na.rm = TRUE), 
    sd = ~sd(., na.rm = TRUE), 
    med = ~median(., na.rm = TRUE), 
    iqr = ~IQR(., na.rm = TRUE))), 
    cor_results = list(tidy(cor.test(BrainAge, ScanAge, use = "complete.obs"))),
    .groups = "drop") %>%
  unnest(cor_results) %>%
  mutate(across(where(is.numeric), ~round(.x, 2))) %>%
  arrange(model, desc(phase)) %>%
  rename(corr_r = estimate) %>%
  rename(corr_lowci = conf.low) %>%
  rename(corr_highci = conf.high) %>%
  select(-statistic, -p.value, -parameter, -method, -alternative)

```

#### Early-Childhood Phase Median/IQR
```{r}

p1_med <- sumtable1 %>%
  ungroup(.) %>%
  filter(phase == "Early-Childhood") %>%
  mutate(Type = ifelse(
    str_detect(model, "phase"), "Phase-Specific", ifelse(
    str_detect(model, "sex"), "Full-Span", NA ))) %>%
  mutate(Model = str_to_upper(str_split_i(model, "_", 3))) %>%
  mutate("Median PAD (IQR)" = paste(BrainPAD_med, " (", BrainPAD_iqr, ")", sep = "")) %>%
  mutate("MAE (IQR)" = paste(AE_med, " (", AE_iqr, ")", sep = "")) %>% 
  mutate("Age r [95% CI]" = paste(corr_r, " [", corr_lowci, ", ", corr_highci, "]", sep = "")) %>%
  select(Model, Type, sex, `Median PAD (IQR)`, `MAE (IQR)`, `Age r [95% CI]`) %>%
  pivot_longer(cols = c(-Model, -Type, -sex), names_to = "Stat", values_to = "Med_IQR") %>%
  pivot_wider(names_from = Model, values_from = Med_IQR) %>%
  select(Stat, sex, Type, S1, S2, F1, A1, A2, A3) %>%
  arrange(desc(Stat), sex, Type) %>%
  gt(rowname_col = "Stat", groupname_col = "sex") %>%
  tab_spanner(
    label = "Model Features", 
    columns = c(S1, S2, F1, A1, A2, A3)
  ) %>%
  tab_stubhead(
    label = "Metric"
  ) %>%
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(rows = Type == "Phase-Specific") 
  )

p1_med

p1_med %>%
  gtsave('/figs/tab_p1med.docx')

```

#### Late-childhood Phase Median/IQR
```{r}

p2_med <- sumtable1 %>%
  ungroup(.) %>%
  filter(phase == "Late-Childhood") %>%
  mutate(Type = ifelse(
    str_detect(model, "phase"), "Phase-Specific", ifelse(
    str_detect(model, "sex"), "Full-Span", NA ))) %>%
  mutate(Model = str_to_upper(str_split_i(model, "_", 3))) %>%
  mutate("Median PAD (IQR)" = paste(BrainPAD_med, " (", BrainPAD_iqr, ")", sep = "")) %>%
  mutate("MAE (IQR)" = paste(AE_med, " (", AE_iqr, ")", sep = "")) %>% 
  mutate("Age r [95% CI]" = paste(corr_r, " [", corr_lowci, ", ", corr_highci, "]", sep = "")) %>%
  select(Model, Type, sex, `Median PAD (IQR)`, `MAE (IQR)`, `Age r [95% CI]`) %>%
  pivot_longer(cols = c(-Model, -Type, -sex), names_to = "Stat", values_to = "Med_IQR") %>%
  pivot_wider(names_from = Model, values_from = Med_IQR) %>%
  select(Stat, sex, Type, S1, S2, F1, A1, A2, A3) %>%
  arrange(desc(Stat), sex, Type) %>%
  gt(rowname_col = "Stat", groupname_col = "sex") %>%
  tab_spanner(
    label = "Model Features", 
    columns = c(S1, S2, F1, A1, A2, A3)
  ) %>%
  tab_stubhead(
    label = "Metric"
  ) %>%
  tab_style(
    style = cell_fill(color = "lightblue"),
    locations = cells_body(rows = Type == "Phase-Specific") 
  )

p2_med

p2_med %>%
  gtsave('/figs/tab_p2med.docx')

```


## Subgroup Comparisons
### Prep
```{r}

source('/scripts/functions/make_reg_tab.R')

cory <- colnames(df.all)[8:19]

```

### BRACO vs SPRESTO/GUSTO
```{r}

gsb <- df.all %>%
  filter(phase == "Early-Childhood") %>%
  mutate(braco = ifelse(ds == "braco", 1, 0)) %>%
  group_by(subjid) %>%
  mutate(id.count = row_number()) %>%
  filter(id.count == 1)

lm0 <- lm(gpb_pred_a3_phase ~ braco*sex + ScanAge, data = gsb)
summary(lm0)

#df.gsb.order <- gsb %>%
#  select(subjid, time) 

#write_csv(df.gsb.order, '/figs/id_order/gsb.order.csv')

```

```{r}

# Use map to run the models and combine them
all_results <- map_df(cory, function(out) {
  formula <- as.formula(paste(out, "~ braco + ScanAge"))
  model <- lm(formula, data = gsb)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
gsb_p <- all_results %>% 
  filter(term == "braco") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))

```

#### Plot
```{r}

fig2a <- gsb_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Early-Childhood: BRACO relative to GUSTO/S-PRESTO",
    subtitle = "N = 359",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2a

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2a.pdf", width=4, height=3)
fig2a
dev.off()
```

#### Table 
```{r}

gsb_tab <- make_reg_tab(gsb_p, "BRACO")

gsb_tab

save_as_docx(gsb_tab, path = '/figs/supp/regression_tab/gsb_one.docx')


```

### YSR
```{r}

ysr_y13 <- read_excel('/original/GUSTO_Y13_YSR 11-18 - Child_20250731.xlsx')

ysr_y13 <- ysr_y13 %>%
  select(subjid, ysr_cage, contains("ss"), contains("dsm"), contains("ysr_2007"),ysr_tot, ysr_tott) %>%
  select(!contains("pct")) %>%
  mutate(ysr_cat = ifelse(ysr_tott > 63, 1, 0))

df.ysr <- merge(df.all, ysr_y13, by = c("subjid"))

df.ysr <- df.ysr %>%
  filter(time == 5)   

lm0 <- lm(gpb_pred_a3_phase ~ ysr_cat*sex + ScanAge, data = df.ysr)
summary(lm0)

df.ysr_m <- df.ysr %>%
  filter(sex == "Male")

df.ysr_f <- df.ysr %>%
  filter(sex == "Female")

```

#### Females
```{r}

# Use map to run the models and combine them
all_results <- map_df(cory, function(out) {
  
  formula <- as.formula(paste(out, "~ ysr_cat + ScanAge"))
  model <- lm(formula, data = df.ysr_f)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ysr_f_p <- all_results %>% 
  filter(term == "ysr_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))


```

#### Female Plot
```{r}

fig2b <- ysr_f_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Females at Y13.5: YSR Total Problems > 63",
    subtitle = "N = 37",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2b

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2b.pdf", width=4, height=3)
fig2b
dev.off()
```

#### Table 
```{r}

ysr_f_tab <- make_reg_tab(ysr_f_p, "High YSR Total (Females)")

ysr_f_tab

save_as_docx(ysr_f_tab, path = '/figs/supp/regression_tab/ysr_f_one.docx')

```

#### Males
```{r}

# Use map to run the models and combine them
all_results <- map_df(cory, function(out) {
  
  formula <- as.formula(paste(out, "~ ysr_cat + ScanAge"))
  model <- lm(formula, data = df.ysr_m)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ysr_m_p <- all_results %>% 
  filter(term == "ysr_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))


```


#### Male Plot
```{r}

fig2c <- ysr_m_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  # Expand the y-axis slightly so labels don't get cut off at the top
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Males at Y13.5: YSR Total Problems > 63",
    subtitle = "N = 44",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2c

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2c.pdf", width=4, height=3)
fig2c
dev.off()
```

#### Table 
```{r}

ysr_m_tab <- make_reg_tab(ysr_m_p, "High YSR Total (Males)")

ysr_m_tab

save_as_docx(ysr_m_tab, path = '/figs/supp/regression_tab/ysr_m_one.docx')

```


### ELA
```{r}

prob.id <- read.csv('/data/prob_ids.csv')

ela <- read.csv('/original/ELA/ela_final.csv')

df.ela <- merge(df.all, ela, by = c("subjid"))

df.ela <- df.ela %>%
  filter(phase == "Early-Childhood") %>%
  group_by(subjid) %>%
  mutate(id.count = row_number()) %>%
  filter(id.count == 1) %>% 
  mutate(ela_cat = ifelse(A_index_prenatal > 2, 1, 0))  

lm0 <- lm(gpb_pred_a3_phase ~ A_index_prenatal*sex + ScanAge, data = df.ela)
summary(lm0)

#df.ela.order <- df.ela %>%
#  select(subjid, time) 

#write_csv(df.ela.order, '/figs/id_order/ela.order.csv')
```

```{r}

# Use map to run the models and combine them
all_results <- map_df(cory, function(out) {
  
  formula <- as.formula(paste(out, "~ A_index_prenatal + ScanAge"))
  model <- lm(formula, data = df.ela)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ela_p <- all_results %>% 
  filter(term == "A_index_prenatal") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))


```

#### Plot
```{r}

fig2d <- ela_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  # Expand the y-axis slightly so labels don't get cut off at the top
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Early-Childhood: Cumulative Early Life Adversity (ELA)",
    subtitle = "N = 93",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2d

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2d.pdf", width=4, height=3)
fig2b
dev.off()
```

#### Table 
```{r}

ela_tab <- make_reg_tab(ela_p, "Cumulative ELA")

ela_tab

save_as_docx(ela_tab, path = '/figs/supp/regression_tab/ela_one.docx')

```

### PSS
```{r}

pss <- read_excel('/original/GUSTO_Y10_PSS_20211215.xlsx')

quantile(pss$pss_totscore, 0.9, na.rm = TRUE)
## 22

pss <- pss %>%
  filter(!is.na(pss_totscore)) %>%
  select(subjid, contains("totscore")) %>%
  mutate(pss_cat = ifelse(pss_totscore > 21, 1, 0))  

df.pss <- merge(df.all, pss, by = c("subjid"))

df.pss <- df.pss %>%
  filter(time == 4)

lm0 <- lm(gpb_pred_a3_phase ~ pss_cat*sex + ScanAge, data = df.pss)
summary(lm0)

df.pss_m <- df.pss %>%
  filter(sex == "Male")

df.pss_f <- df.pss %>%
  filter(sex == "Female") 

```

```{r}

# Use map (a better for-loop) to run the models and combine them
all_results <- map_df(cory, function(out) {

  formula <- as.formula(paste(out, "~ pss_cat + ScanAge"))
  model <- lm(formula, data = df.pss_f)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_f_p <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))


```

#### Female Plot
```{r}

fig2e <- pss_f_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  # Expand the y-axis slightly so labels don't get cut off at the top
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Females at Y10.5: PSS Total Score > 21",
    subtitle = "N = 40",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2e

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2e.pdf", width=4, height=3)
fig2e
dev.off()
```

#### Table 
```{r}

pss_f_tab <- make_reg_tab(pss_f_p, "High PSS (Females)")

pss_f_tab

save_as_docx(pss_f_tab, path = '/figs/supp/regression_tab/pss_f_one.docx')

```


```{r}

# Use map (a better for-loop) to run the models and combine them
all_results <- map_df(cory, function(out) {

  formula <- as.formula(paste(out, "~ pss_cat + ScanAge"))
  model <- lm(formula, data = df.pss_m)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_m_p <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(model = outcome_var) %>%
  mutate(model = str_replace(model, fixed("gpb_pred_"), ""))  %>%
  separate(model, c("Feature", "Type"), "_") %>%
  mutate(Feature = toupper(Feature)) %>%
  mutate(Type = ifelse(
    Type == "sex", "Full-Span", ifelse(
    Type == "phase", "Phase-Specific", Type
  ))) %>%
  mutate(Feature = factor(Feature, levels = rev(c("S1", "S2", "F1", "A1", "A2", "A3")))) %>%
  mutate(Type = factor(Type, levels = c("Full-Span", "Phase-Specific")))


```

#### Male Plot
```{r}

fig2f <- pss_m_p %>%
  ggplot(aes(x = estimate, y = Feature)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + # Null line
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  facet_grid(Type ~ ., scales = "free_y", space = "free_y") + 
  # Expand the y-axis slightly so labels don't get cut off at the top
  scale_y_discrete(expand = expansion(add = c(0.5, 1))) +
  theme_minimal(base_size = 8) +  
  labs(
    title = "Males at Y10.5: PSS Total Score > 21",
    subtitle = "N = 55",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    panel.spacing = unit(1, "lines"),         # Adds a bit of gap between groups
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig2f

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig2f.pdf", width=4, height=3)
fig2f
dev.off()
```

#### Table 
```{r}

pss_m_tab <- make_reg_tab(pss_m_p, "High PSS (Males)")

pss_m_tab

save_as_docx(pss_m_tab, path = '/figs/supp/regression_tab/pss_m_one.docx')

```
