---
title: "Results Three - Benchmarking Clean"
author: "SYC"
date: "2026-05-02"
output: html_document
---

## Packages
```{r}
library(gt)
library(flextable)
library(officer)
library(patchwork)
library(broom)
library(stringr)
library(purrr)
library(readr)
library(Hmisc)
library(corrplot)
library(ggplot2)
library(ggdist)
library(tidyr)
library(dplyr)

```

## Load data
**Phase-Specific Models + BrainAge models from the literature**
```{r}

ba.all <- read_csv('/Users/chansy1/Dropbox/Mac (3)/Documents/projects/brainage/july2025/output/brainage_compiled.csv')

```

### Exclusions
```{r}

## missing data from 2 scans 
ba.all_rm <- ba.all %>%
  filter(!(subjid == "010-21794" & time == 1)) %>%
  filter(!(subjid == "020-66082" & time == 2)) %>%
  arrange(sex)

```


## Raincloud Plots 
```{r}

plot.ba <- ba.all_rm %>%
  select(1:6, sex, phase, gpb_pred_a2, ENIGMA_predage, centile_MR_predicted_age, DevBrainAge_predage, PyBrainAge_predage) %>%
  gather(key = "model", value = "brain.age", -subjid, -id, -ScanAge, -time, -batch, -ds, -sex, -phase)  %>%
  mutate(Timepoint = as.character(time) %>%
           fct_recode(
    "GUSTO_4.5YO" = "1",
    "GUSTO_6.0YO" = "2",
    "GUSTO_7.5YO" = "3",
    "GUSTO_10.5YO" = "4",
    "GUSTO_13.0YO" = "5",
    "BRACO/SPRESTO" = "6") %>%
      fct_relevel("GUSTO_4.5YO", "GUSTO_6.0YO", "GUSTO_7.5YO", "GUSTO_10.5YO", "GUSTO_13.0YO", "BRACO/SPRESTO")) %>%
  mutate(Model = model %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("Phase-Specific_A2", "ENIGMA", "Centile", "DevBrainAge", "PyBrainAge"))  

```

### Males Early Childhood
```{r}

# 1. Define specific settings for each model
model_configs <- list(
  "Phase-Specific_A2" = c(bin = 0.15, dsize = 0.6),
  "ENIGMA" = c(bin = 0.35, dsize = 1.4),
  "Centile" = c(bin = 0.2, dsize = 1.1),
  "DevBrainAge" = c(bin = 0.2, dsize = 1),
  "PyBrainAge" = c(bin = 0.5, dsize = 1.5)
)

# 2. Function for each individual facet
make_raincloud <- function(model_name, config_values) {
  first_model <- names(model_configs)[1]
  bin <- config_values["bin"]
  dsize <- config_values["dsize"]
  
  p.df <- plot.ba %>%
    filter(sex == "Male") %>%
    filter(phase == "Early-Childhood") %>%
    filter(Model == model_name)
  
  p <- p.df %>%
    ggplot(aes(x = Timepoint, y = brain.age)) +
    # The Cloud
    stat_halfeye(
      adjust = 0.5,
      justification = -.2,
      .width = 0, 
      point_colour = NA,
      alpha = 0.5,
      scale = 0.6 # Keeps cloud height consistent
    ) + 
    # The Boxplot
    geom_boxplot(
      width = .12,
      alpha = 0.5,
      outlier.size = 0.5
    ) + 
    # The Rain 
    stat_dots(
      aes(x = Timepoint, y = ScanAge), 
      side = "left", 
      justification = 1.1,
      binwidth = bin,
      dotsize = dsize,
      stackratio = 0.5,
      scale = 0.6,
      layout = "hex",
      alpha = 0.7, 
      color =  "#C8A88AFF"
    ) + 
    coord_flip() +
    labs(title = model_name) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      panel.grid.minor = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(), 
      plot.title = element_text(
        size = 9, 
        hjust = 0.5
      ), 
      plot.margin = margin(t = 3, r = 2, b = 3, l = 2)
    ) 
  
  if (model_name != first_model) {
    p <- p + theme(
      axis.text.y = element_blank(),   
      axis.ticks.y = element_blank(),  
      axis.title.y = element_blank()   
    )
  }
  return(p)
}

# 3. Generate the list of plots
all_plots <- mapply(make_raincloud, 
                    model_name = names(model_configs), 
                    config_values = model_configs, 
                    SIMPLIFY = FALSE)

# 4. Stitch them together
# ncol = 5 puts them all in one row
p1m <- wrap_plots(all_plots, ncol = 5) + 
  plot_annotation(title = "Males: Early-childhood phase",
                  caption = "Predicted Brain Age (Years)",
                  theme = theme(
                    plot.title = element_text(
                      family = "Helvetica", 
                      face = "bold",
                      hjust = 0.5, 
                      size = 11
                      ), 
                    plot.caption = element_text(
                      family = "Helvetica", 
                      hjust = 0.5
                      )
                    )
  ) + 
  theme(
    panel.spacing = unit(0.3, "lines"), 
    plot.margin = margin(t = 4, r = 1.5, b = 4, l = 1.5) 
  )

# 5. Display or Save
print(p1m)

```

#### Save
```{r}
setwd('/figs')

pdf(file="fig4_p1m.pdf", width = 8.5, height = 3.6)
p1m
dev.off()
```

### Females Early-Childhood
```{r}

# 1. Define specific settings for each model
model_configs <- list(
  "Phase-Specific_A2" = c(bin = 0.15, dsize = 0.6),
  "ENIGMA" = c(bin = 0.35, dsize = 1.4),
  "Centile" = c(bin = 0.2, dsize = 1.1),
  "DevBrainAge" = c(bin = 0.2, dsize = 1),
  "PyBrainAge" = c(bin = 0.5, dsize = 1.5)
)

# 2. Function for each individual facet
make_raincloud <- function(model_name, config_values) {
  first_model <- names(model_configs)[1]
  bin <- config_values["bin"]
  dsize <- config_values["dsize"]
  
  p.df <- plot.ba %>%
    filter(sex == "Female") %>%
    filter(phase == "Early-Childhood") %>%
    filter(Model == model_name)
  
  p <- p.df %>%
    ggplot(aes(x = Timepoint, y = brain.age)) +
    # The Cloud
    stat_halfeye(
      adjust = 0.5,
      justification = -.2,
      .width = 0, 
      point_colour = NA,
      alpha = 0.5,
      scale = 0.6 # Keeps cloud height consistent
    ) + 
    # The Boxplot
    geom_boxplot(
      width = .12,
      alpha = 0.5,
      outlier.size = 0.5
    ) + 
    # The Rain 
    stat_dots(
      aes(x = Timepoint, y = ScanAge), 
      side = "left", 
      justification = 1.1,
      binwidth = bin,
      dotsize = dsize,
      stackratio = 0.5,
      scale = 0.6,
      layout = "hex",
      alpha = 0.7, 
      color =  "#C8A88AFF"
    ) + 
    coord_flip() +
    labs(title = model_name) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      panel.grid.minor = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(), 
      plot.title = element_text(
        size = 9, 
        hjust = 0.5
      ), 
      plot.margin = margin(t = 3, r = 2, b = 3, l = 2)
    ) 
  
  if (model_name != first_model) {
    p <- p + theme(
      axis.text.y = element_blank(),   
      axis.ticks.y = element_blank(),  
      axis.title.y = element_blank()   
    )
  }
  return(p)
}

# 3. Generate the list of plots
all_plots <- mapply(make_raincloud, 
                    model_name = names(model_configs), 
                    config_values = model_configs, 
                    SIMPLIFY = FALSE)

# 4. Stitch them together
# ncol = 5 puts them all in one row
p1f <- wrap_plots(all_plots, ncol = 5) + 
  plot_annotation(title = "Females: Early-childhood phase",
                  caption = "Predicted Brain Age (Years)",
                  theme = theme(
                    plot.title = element_text(
                      family = "Helvetica", 
                      face = "bold",
                      hjust = 0.5, 
                      size = 11
                      ), 
                    plot.caption = element_text(
                      family = "Helvetica", 
                      hjust = 0.5
                      )
                    )
  ) + 
  theme(
    panel.spacing = unit(0.3, "lines"), 
    plot.margin = margin(t = 4, r = 1.5, b = 4, l = 1.5) 
  )

# 5. Display or Save
print(p1f)

```

#### Save
```{r}
setwd('/figs')

pdf(file="fig4_p1f.pdf", width = 8.5, height = 3.6)
p1f
dev.off()
```


### Males Late-childhood
```{r}

# 1. Define specific settings for each model
model_configs <- list(
  "Phase-Specific_A2" = c(bin = 0.15, dsize = 0.6),
  "ENIGMA" = c(bin = 0.35, dsize = 1.4),
  "Centile" = c(bin = 0.2, dsize = 1.1),
  "DevBrainAge" = c(bin = 0.2, dsize = 1),
  "PyBrainAge" = c(bin = 0.5, dsize = 1.5)
)

# 2. Function for each individual facet
make_raincloud <- function(model_name, config_values) {
  first_model <- names(model_configs)[1]
  bin <- config_values["bin"]
  dsize <- config_values["dsize"]
  
  p.df <- plot.ba %>%
    filter(sex == "Male") %>%
    filter(phase == "Late-Childhood") %>%
    filter(Model == model_name)
  
  p <- p.df %>%
    ggplot(aes(x = Timepoint, y = brain.age)) +
    # The Cloud
    stat_halfeye(
      adjust = 0.5,
      justification = -.2,
      .width = 0, 
      point_colour = NA,
      alpha = 0.5,
      scale = 0.6 
    ) + 
    # The Boxplot
    geom_boxplot(
      width = .12,
      alpha = 0.5,
      outlier.size = 0.5
    ) + 
    # The Rain 
    stat_dots(
      aes(x = Timepoint, y = ScanAge), 
      side = "left", 
      justification = 1.1,
      binwidth = bin,
      dotsize = dsize,
      stackratio = 0.5,
      scale = 0.6,
      layout = "hex",
      alpha = 0.7, 
      color =  "#C8A88AFF"
    ) + 
    coord_flip() +
    labs(title = model_name) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      panel.grid.minor = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(), 
      plot.title = element_text(
        size = 9, 
        hjust = 0.5
      ), 
      plot.margin = margin(t = 3, r = 2, b = 3, l = 2)
    ) 
  
  if (model_name != first_model) {
    p <- p + theme(
      axis.text.y = element_blank(),   
      axis.ticks.y = element_blank(),  
      axis.title.y = element_blank()   
    )
  }
  return(p)
}

# 3. Generate the list of plots
all_plots <- mapply(make_raincloud, 
                    model_name = names(model_configs), 
                    config_values = model_configs, 
                    SIMPLIFY = FALSE)

# 4. Stitch them together
# ncol = 5 puts them all in one row
p2m <- wrap_plots(all_plots, ncol = 5) + 
  plot_annotation(title = "Males: Late-childhood phase",
                  caption = "Predicted Brain Age (Years)",
                  theme = theme(
                    plot.title = element_text(
                      family = "Helvetica", 
                      face = "bold",
                      hjust = 0.5, 
                      size = 11
                      ), 
                    plot.caption = element_text(
                      family = "Helvetica", 
                      hjust = 0.5
                      )
                    )
  ) + 
  theme(
    panel.spacing = unit(0.3, "lines"), 
    plot.margin = margin(t = 4, r = 1.5, b = 4, l = 1.5) 
  )

# 5. Display or Save
print(p2m)

```

#### Save
```{r}
setwd('/figs')

pdf(file="fig4_p2m.pdf", width = 8.5, height = 3)
p2m
dev.off()
```


### Females Late-childhood
```{r}

# 1. Define specific settings for each model
model_configs <- list(
  "Phase-Specific_A2" = c(bin = 0.15, dsize = 0.6),
  "ENIGMA" = c(bin = 0.35, dsize = 1.4),
  "Centile" = c(bin = 0.2, dsize = 1.1),
  "DevBrainAge" = c(bin = 0.2, dsize = 1),
  "PyBrainAge" = c(bin = 0.5, dsize = 1.5)
)

# 2. Function for each individual facet
make_raincloud <- function(model_name, config_values) {
  first_model <- names(model_configs)[1]
  bin <- config_values["bin"]
  dsize <- config_values["dsize"]
  
  p.df <- plot.ba %>%
    filter(sex == "Female") %>%
    filter(phase == "Late-Childhood") %>%
    filter(Model == model_name)
  
  p <- p.df %>%
    ggplot(aes(x = Timepoint, y = brain.age)) +
    # The Cloud
    stat_halfeye(
      adjust = 0.5,
      justification = -.2,
      .width = 0, 
      point_colour = NA,
      alpha = 0.5,
      scale = 0.6 
    ) + 
    # The Boxplot
    geom_boxplot(
      width = .12,
      alpha = 0.5,
      outlier.size = 0.5
    ) + 
    # The Rain 
    stat_dots(
      aes(x = Timepoint, y = ScanAge), 
      side = "left", 
      justification = 1.1,
      binwidth = bin,
      dotsize = dsize,
      stackratio = 0.5,
      scale = 0.6,
      layout = "hex",
      alpha = 0.7, 
      color =  "#C8A88AFF"
    ) + 
    coord_flip() +
    labs(title = model_name) +
    theme_minimal(base_family = "Helvetica") +
    theme(
      panel.grid.minor = element_blank(),
      axis.title.y = element_blank(),
      axis.title.x = element_blank(), 
      plot.title = element_text(
        size = 9, 
        hjust = 0.5
      ), 
      plot.margin = margin(t = 3, r = 2, b = 3, l = 2)
    ) 
  
  if (model_name != first_model) {
    p <- p + theme(
      axis.text.y = element_blank(),   
      axis.ticks.y = element_blank(),  
      axis.title.y = element_blank()   
    )
  }
  return(p)
}

# 3. Generate the list of plots
all_plots <- mapply(make_raincloud, 
                    model_name = names(model_configs), 
                    config_values = model_configs, 
                    SIMPLIFY = FALSE)

# 4. Stitch them together
# ncol = 5 puts them all in one row
p2f <- wrap_plots(all_plots, ncol = 5) + 
  plot_annotation(title = "Females: Late-childhood phase",
                  caption = "Predicted Brain Age (Years)",
                  theme = theme(
                    plot.title = element_text(
                      family = "Helvetica", 
                      face = "bold",
                      hjust = 0.5, 
                      size = 11
                      ), 
                    plot.caption = element_text(
                      family = "Helvetica", 
                      hjust = 0.5
                      )
                    )
  ) + 
  theme(
    panel.spacing = unit(0.3, "lines"), 
    plot.margin = margin(t = 4, r = 1.5, b = 4, l = 1.5) 
  )

# 5. Display or Save
print(p2f)

```

#### Save
```{r}
setwd('/figs')

pdf(file="fig4_p2f.pdf", width = 8.5, height = 3)
p2f
dev.off()
```

## Supp Table S6 
```{r}

tab.ba <- ba.all_rm %>%
  select(1:6, sex, phase, gpb_pred_a2, ENIGMA_predage, centile_MR_predicted_age, DevBrainAge_predage, PyBrainAge_predage) %>%
  gather(key = "model", value = "BrainAge", -subjid, -id, -ScanAge, -time, -batch, -ds, -sex, -phase)  %>%
  mutate(BrainPAD = BrainAge - ScanAge) %>%
  mutate(AE = abs(ScanAge - BrainAge)) %>%
  mutate(Model = model %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("Phase-Specific_A2", "ENIGMA", "Centile", "DevBrainAge", "PyBrainAge"))  


sumtable1 <- tab.ba %>%
  group_by(Model, sex, phase) %>%
  summarise(across(c(BrainAge, BrainPAD, AE), list(
    mean = ~mean(., na.rm = TRUE), 
    sd = ~sd(., na.rm = TRUE), 
    med = ~median(., na.rm = TRUE), 
    iqr = ~IQR(., na.rm = TRUE))), 
    cor_results = list(tidy(cor.test(BrainAge, ScanAge, use = "complete.obs"))),
    .groups = "drop") %>%
  unnest(cor_results) %>%
  mutate(across(where(is.numeric), ~round(.x, 2))) %>%
  arrange(Model, desc(phase)) %>%
  rename(corr_r = estimate) %>%
  rename(corr_lowci = conf.low) %>%
  rename(corr_highci = conf.high) %>%
  select(-statistic, -p.value, -parameter, -method, -alternative)

```

```{r}

ba_tab_med <- sumtable1 %>%
  ungroup(.) %>%
  mutate("Median PAD (IQR)" = paste(BrainPAD_med, " (", BrainPAD_iqr, ")", sep = "")) %>%
  mutate("MAE (IQR)" = paste(AE_med, " (", AE_iqr, ")", sep = "")) %>% 
  mutate("Age r [95% CI]" = paste(corr_r, " [", corr_lowci, ", ", corr_highci, "]", sep = "")) %>%
  select(Model, Phase, sex, `Median PAD (IQR)`, `MAE (IQR)`, `Age r [95% CI]`) %>%
  pivot_longer(cols = c(-Model, -sex, -Phase), names_to = "Stat", values_to = "Med_IQR") %>%
  pivot_wider(names_from = Model, values_from = Med_IQR) %>%
  rename(Sex = sex) %>%
  gt(rowname_col = "Stat", groupname_col = "Phase") %>%
  tab_spanner(
    label = "BrainAge Estimates", 
    columns = c(`Phase-Specific_A2`, ENIGMA, Centile, DevBrainAge, PyBrainAge)
  ) %>%  
  tab_stubhead(
    label = "Metric"
  ) 

ba_tab_med

ba_tab_med %>%
  gtsave('/figs/tab_balit_med.docx')


```

## Subgroup Comparisons
### Prep
```{r}

source('/scripts/functions/make_reg_tab_three.R')

```

### Demo
```{r}

demo <- read.csv('/original/GUSTO_Gender & Ethnicity_Jasmine.csv')

demo <- demo %>%
  rename(sex = csex) %>%
  rename(mother_ethnicity = mrace) %>%
  select(subjid, sex) %>%
  na.omit()

demo2 <- read.csv('/braco-ld/data/oct2025/BRACO_Y4-6_age_20260128.csv')

demo2 <- demo2 %>%
  select(subjid, sex) %>%
  mutate(sex = ifelse(sex == 1, "Male", ifelse(sex == 2, "Female", NA)))

demo <- rbind(demo, demo2)

rm(demo2)
```

### Add Biological Age
```{r}

bage.pred <- c("PEDBE", "transform.telolength")

dnam <- read.csv('/data/dnam_norep_minfi.csv')

dnam <- dnam %>%
  mutate(time = case_when(
    ds == "gusto_m54" ~ 1,
    ds == "gusto_y6" ~ 2,
    ds == "gusto_y7.5" ~ 3,
    ds == "gusto_y10.5" ~ 4,   
    ds == "braco_ld" ~ 6,
    ds == "braco_p" ~ 6,
    .default = NA
  )) %>%
  rename(BucAge = Age) %>%
  mutate(ds = ifelse(
    str_detect(ds, "gusto"), "gusto", ifelse(
    str_detect(ds, "braco"), "braco", NA
    ))) %>%
  select(subjid, time, ds, BucAge, PEDBE) 

telo <- read.csv('/data/telomerelength/output/telo_clean_jan2026.csv')

telo <- telo %>%
  select(subjid, time, ds, buc.age, Transform.Telomere..B.Globin) %>%
  mutate(ds = ifelse(
    str_detect(ds, "gusto"), "gusto", ifelse(
    str_detect(ds, "braco"), "braco", NA
    ))) %>%  
  rename(transform.telolength = Transform.Telomere..B.Globin) %>%
  rename(BucAge = buc.age) 

bage <- merge(dnam, telo, by = c("subjid", "time", "BucAge", "ds"), all = TRUE)

bage2 <- merge(bage, demo, by = c("subjid"), all.x = TRUE)

bage2.1 <- bage2 %>%
  filter(time < 4 | time == 6) %>%
  mutate(phase = "Early-Childhood")

bage2.2 <- bage2 %>%
  filter(time == 3 | time == 4 | time == 5) %>%
  mutate(phase = "Late-Childhood")

bage2_wrep <- rbind(bage2.1, bage2.2)  

```

### BrainAge Prep
```{r}

age.pred <- c("gpb_pred_a2", "ENIGMA_predage", "centile_MR_predicted_age", "DevBrainAge_predage", "PyBrainAge_predage")

ba.all2 <- ba.all_rm %>%
  select(subjid, id, ScanAge, time, batch, ds, sex, all_of(age.pred), phase)

```

### BRACO vs SPRESTO/GUSTO
```{r}

gsb.order <- read_csv('/figs/id_order/gsb.order.csv')

gsb.order <- gsb.order %>%
  ungroup(.) %>%
  mutate(order = row_number())

gsb_1 <- merge(gsb.order, ba.all2, by = c("subjid", "time"), all.x = TRUE)

gsb_1 <- gsb_1 %>%
  filter(phase == "Early-Childhood") %>%
  mutate(braco = ifelse(ds == "braco", 1, 0)) 

gsb_2 <- bage2_wrep %>%
  filter(phase == "Early-Childhood") %>%
  mutate(braco = ifelse(ds == "braco", 1, 0)) %>%
  group_by(subjid) %>%
  mutate(id.count = row_number()) %>%
  filter(id.count == 1)
  
```

#### BrainAge
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {

  formula <- as.formula(paste(out, "~ braco + ScanAge"))
  model <- lm(formula, data = gsb_1)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
gsb_p <- all_results %>% 
  filter(term == "braco") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### BioAge
```{r}

# Use map to run the models and combine them
all_results <- map_df(bage.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ braco + BucAge"))
  model <- lm(formula, data = gsb_2)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
gsb_p2 <- all_results %>% 
  filter(term == "braco") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "PedBE" = "PEDBE",    
    "TeloLength" = "transform.telolength") %>%
      fct_relevel("TeloLength", "PedBE")) 

gsb_p <- rbind(gsb_p2, gsb_p)

```

#### Plot
```{r}

fig_gsb <- gsb_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) +  
  labs(
    title = "Early-Childhood: BRACO relative to GUSTO/S-PRESTO",
    subtitle = "n = 357",
    x = "Regression Coefficient (95% CI)",
    y = "Model"
  ) + 
  theme(            
#    panel.spacing = unit(0.5, "lines"), 
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_gsb

```
#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_gsb.pdf", width=4, height=2)
fig_gsb
dev.off()
```

#### Table 
```{r}

gsb_tab <- make_reg_tab(gsb_p, "BRACO")

gsb_tab

save_as_docx(gsb_tab, path = '/figs/supp/regression_tab/gsb_three.docx')

```


### YSR
```{r}

ysr_y13 <- read_excel('/original/GUSTO_Y13_YSR 11-18 - Child_20250731.xlsx')

ysr_y13 <- ysr_y13 %>%
  select(subjid, ysr_cage, contains("ss"), contains("dsm"), contains("ysr_2007"),ysr_tot, ysr_tott) %>%
  select(!contains("pct")) %>%
  mutate(ysr_cat = ifelse(ysr_tott > 63, 1, 0))

df.ysr_1 <- merge(ba.all2, ysr_y13, by = c("subjid"))

df.ysr_m <- df.ysr_1 %>%
  filter(time == 5) %>%
  filter(sex == "Male")

df.ysr_f <- df.ysr_1 %>%
  filter(time == 5) %>%
  filter(sex == "Female")

```

#### BrainAge - Female
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ ysr_cat + ScanAge"))
  model <- lm(formula, data = df.ysr_f)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ysr_f_p <- all_results %>% 
  filter(term == "ysr_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### Female Plot
```{r}

fig_ysr_f <- ysr_f_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) +  
  labs(
    title = "Females at Y13.5: YSR Total Problems > 63",
    subtitle = "N = 37",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_ysr_f

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_ysr_f.pdf", width=4, height=1.7)
fig_ysr_f
dev.off()
```

#### Table 
```{r}

ysr_f_tab <- make_reg_tab(ysr_f_p, "High YSR Total (Females)")

ysr_f_tab

save_as_docx(ysr_f_tab, path = '/figs/supp/regression_tab/ysr_f_three.docx')

```

#### BrainAge - Male
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ ysr_cat + ScanAge"))
  model <- lm(formula, data = df.ysr_m)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ysr_m_p <- all_results %>% 
  filter(term == "ysr_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### Male Plot
```{r}

fig_ysr_m <- ysr_m_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) +  
  labs(
    title = "Males at Y13.5: YSR Total Problems > 63",
    subtitle = "N = 44",
    x = "Regression Coefficient (95% CI)",
    y = "BrainAge Model"
  ) + 
  theme(            
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_ysr_m

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_ysr_m.pdf", width=4, height=1.7)
fig_ysr_m
dev.off()
```

#### Table 
```{r}

ysr_m_tab <- make_reg_tab(ysr_m_p, "High YSR Total (Males)")

ysr_m_tab

save_as_docx(ysr_m_tab, path = '/figs/supp/regression_tab/ysr_m_three.docx')

```

### ELA
```{r}

ela <- read.csv('/original/ELA/ela_final.csv')

ela.order <- read_csv('/figs/id_order/ela.order.csv')

ela.order <- ela.order %>%
  ungroup(.) %>%
  mutate(order = row_number())

ela_1 <- merge(ba.all2, ela, by = c("subjid"))
ela_1 <- merge(ela.order, ela_1, by = c("subjid", "time"), all.x = TRUE)
ela_1 <- ela_1 %>%
  dplyr::filter(phase == "Early-Childhood")

ela_2 <- merge(bage2_wrep, ela, by = c("subjid"))
ela_2 <- ela_2 %>%
  filter(phase == "Early-Childhood") %>%
  group_by(subjid) %>%
  mutate(id.count = row_number()) %>%
  filter(id.count == 1) 

```

#### BrainAge
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ A_index_prenatal + ScanAge"))
  model <- lm(formula, data = ela_1)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ela_p <- all_results %>% 
  filter(term == "A_index_prenatal") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### BioAge
```{r}

# Use map to run the models and combine them
all_results <- map_df(bage.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ A_index_prenatal + BucAge"))
  model <- lm(formula, data = ela_2)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
ela_p2 <- all_results %>% 
  filter(term == "A_index_prenatal") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "PedBE" = "PEDBE",    
    "TeloLength" = "transform.telolength") %>%
      fct_relevel("TeloLength", "PedBE")) 

ela_p <- rbind(ela_p2, ela_p)

```

#### Plot
```{r}

fig_ela <- ela_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) + 
  labs(
    title = "Early-Childhood: Cumulative Early Life Adversity (ELA)",
    subtitle = "n = 91",
    x = "Regression Coefficient (95% CI)",
    y = "Model"
  ) + 
  theme(            
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_ela

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_ela.pdf", width=4, height=2)
fig_ela
dev.off()
```

#### Table 
```{r}

ela_tab <- make_reg_tab(ela_p, "Cumulative ELA")

ela_tab

save_as_docx(ela_tab, path = '/figs/supp/regression_tab/ela_three.docx')

```

### PSS
```{r}

pss <- read_excel('/original/GUSTO_Y10_PSS_20211215.xlsx')

pss <- pss %>%
  filter(!is.na(pss_totscore)) %>%
  select(subjid, contains("totscore")) %>%
  mutate(pss_cat = ifelse(pss_totscore > 21, 1, 0))  

df.pss_1 <- merge(ba.all2, pss, by = c("subjid"))

df.pss_m <- df.pss_1 %>%
  filter(time == 4) %>%
  filter(sex == "Male")

df.pss_f <- df.pss_1 %>%
  filter(time == 4) %>%
  filter(sex == "Female") 

df.pss_2 <- merge(bage2_wrep, pss, by = c("subjid"))

df.pss_m2 <- df.pss_2 %>%
  filter(time == 4) %>%
  filter(sex == "Male")

df.pss_f2 <- df.pss_2 %>%
  filter(time == 4) %>%
  filter(sex == "Female") 

```

#### BrainAge - Female
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ pss_cat + ScanAge"))
  model <- lm(formula, data = df.pss_f)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_f_p <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### BioAge - Female
```{r}

# Use map (a better for-loop) to run the models and combine them
all_results <- map_df(bage.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ pss_cat + BucAge"))
  model <- lm(formula, data = df.pss_f2)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_f_p2 <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "PedBE" = "PEDBE",    
    "TeloLength" = "transform.telolength") %>%
      fct_relevel("TeloLength", "PedBE")) 

pss_f_p  <- rbind(pss_f_p2, pss_f_p)

```

#### Female Plot
```{r}

fig_pss_f <- pss_f_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) +  
  labs(
    title = "Females at Y10.5: PSS Total Score > 21",
    subtitle = "N = 40",
    x = "Regression Coefficient (95% CI)",
    y = "Model"
  ) + 
  theme(            
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_pss_f

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_pss_f.pdf", width=4, height=2)
fig_pss_f
dev.off()
```

#### Table 
```{r}

pss_f_tab <- make_reg_tab(pss_f_p, "High PSS (Females)")

pss_f_tab

save_as_docx(pss_f_tab, path = '/figs/supp/regression_tab/pss_f_three.docx')

```

#### BrainAge - Male
```{r}

# Use map to run the models and combine them
all_results <- map_df(age.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ pss_cat + ScanAge"))
  model <- lm(formula, data = df.pss_m)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_m_p <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "Phase-Specific_A2" = "gpb_pred_a2",    
    "ENIGMA" = "ENIGMA_predage",
    "Centile" = "centile_MR_predicted_age",
    "DevBrainAge" = "DevBrainAge_predage",
    "PyBrainAge" = "PyBrainAge_predage") %>%
      fct_relevel("PyBrainAge", "DevBrainAge", "Centile", "ENIGMA", "Phase-Specific_A2")) 

```

#### BioAge - Male
```{r}

# Use map to run the models and combine them
all_results <- map_df(bage.pred, function(out) {
  
  formula <- as.formula(paste(out, "~ pss_cat + BucAge"))
  model <- lm(formula, data = df.pss_m2)
  
  # Turn the model results into a data frame
  tidy(model, conf.int = TRUE) %>%
    mutate(outcome_var = out) 
})

# Filter to show ONLY the 'Group' effect across all outcomes
pss_m_p2 <- all_results %>% 
  filter(term == "pss_cat") %>%
  mutate(
    p_label = ifelse(p.value < .001, "p < .001", paste0("p = ", round(p.value, 3))),
    is_sig = ifelse(p.value < 0.05, "bold", "plain")
  ) %>%
  mutate(Model = outcome_var %>%
           fct_recode(
    "PedBE" = "PEDBE",    
    "TeloLength" = "transform.telolength") %>%
      fct_relevel("TeloLength", "PedBE")) 

pss_m_p  <- rbind(pss_m_p2, pss_m_p)

```

#### Male Plot
```{r}

fig_pss_m <- pss_m_p %>%
  ggplot(aes(x = estimate, y = Model)) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "red") + 
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.1) +
  geom_point(size = 2.2, color = "midnightblue", shape = 18) +
  geom_text(aes(label = p_label, fontface = is_sig), 
            vjust = -1, size = 2) +
  scale_y_discrete(expand = expansion(add = c(0.5, 0.8))) +   
  theme_minimal(base_size = 8) +  
  labs(
    title = "Males at Y10.5: PSS Total Score > 21",
    subtitle = "N = 55",
    x = "Regression Coefficient (95% CI)",
    y = "Model"
  ) + 
  theme(            
    plot.title = element_text(hjust = 0.5),
    plot.subtitle = element_text(hjust = 0.5, face = "italic")  
    ) 

fig_pss_m

```

#### Save
```{r}
setwd('/figs')

pdf(file="fplot_fig4b_pss_m.pdf", width=4, height=2)
fig_pss_m
dev.off()
```

#### Table 
```{r}

pss_m_tab <- make_reg_tab(pss_m_p, "High PSS (Males)")

pss_m_tab

save_as_docx(pss_m_tab, path = '/figs/supp/regression_tab/pss_m_three.docx')

```

