---
title: "Supp - Sensitivity Analyses - Motion Subset Models"
author: "SYC"
date: "2026-05-02"
output: html_document
---

```{r}

library(caret)
library(gt)
library(patchwork)
library(forestplot)
library(gpboost)
library(SHAPforxgboost)
library(ggplot2)
library(ggdist)
library(purrr)
library(readxl)
library(readr)
library(tidyr)
library(stringr)
library(dplyr)

```

```{r}

calc_outliers <- function(data_column) {
  Q1 <- quantile(data_column, 0.25)
  IQR <- IQR(data_column)
  lower_limit <- Q1 - 1.5 * IQR
  return(lower_limit)
}

```

## Make Exclusion List
```{r}

qc_fs_vis <- read_csv('/data/fsvisqc_all.csv')

qc_fs <- read_csv('/data/euler_all.csv')

qc_conn <- read_csv('/data/connqc_all.csv')

qc <- merge(qc_fs, qc_fs_vis, by = c("subjid", "ds"))
qc <- merge(qc, qc_conn, by = c("subjid", "ds"))

qc <- qc %>%
  select(subjid, ds, euler, fs_visQC, QC_MeanMotion, QC_InvalidScans) %>%
  mutate(time = case_when(
    ds == "gusto_m54" ~ 1,
    ds == "gusto_y6" ~ 2,
    ds == "gusto_y7" ~ 3,
    ds == "gusto_y10" ~ 4, 
    ds == "gusto_y13" ~ 5, 
    ds == "braco" | ds == "spresto" ~ 6,
    .default = NA))

```

### Exclude FS
```{r}

euler_outliers <- qc %>%
  select(ds, euler) %>%
  group_by(ds) %>%
  mutate(eul_low = calc_outliers(euler)) %>%
  select(ds, eul_low) %>%
  unique()
  
qc <- merge(qc, euler_outliers, by = c("ds"), all.x = TRUE)  

qc <- qc %>%
  mutate(eul_out = ifelse(
    euler < eul_low, 1, 0
  ))
  
fs_exc <- qc %>%
  filter(eul_out == 1 & fs_visQC == 0) %>%
  select(subjid, ds, time) %>%
  mutate(fs_exc = 1)

## N = 43 excluded 

```

### Exclude CONN
```{r}

## site 1 & Y7.5 - 120 volumes
##(116*0.25+4) = 33; invalid scans > 33 = exclude

## Y10.5 - 183 volumes
## (179*0.25+4) = 48.75; invalid scans > 49 = exclude

## Y13 - 114 volumes
## (110*0.25+4) = 31.5; invalid scans > 32 = exclude

## site 3 - multiband 668 volumes
##(664*0.25 + 4) = 170; invalid scans > 170 = exclude 

conn_outliers <- data.frame(ds = euler_outliers$ds, conn_limit = c(33, 49, 32, 33, 33, 170, 170))
  
qc <- merge(qc, conn_outliers, by = c("ds"), all.x = TRUE)  

qc <- qc %>%
  mutate(conn_out = ifelse(
    QC_InvalidScans > conn_limit, 1, 0
  ))

conn_exc <- qc %>%
  filter(conn_out == 1) %>%
  select(subjid, ds, time) %>%
  mutate(conn_exc = 1)

## N = 288

conn_exc <- conn_exc %>%
  arrange(time, subjid)

## ID with only 6 scan volumes
addid <- data.frame(subjid = "010-14055", ds = "gusto_y10", time = 4, conn_exc = 1)

conn_exc <- rbind(conn_exc, addid)

table(conn_exc$ds)

```

### Merge Both
```{r}

exc.list <- merge(conn_exc, fs_exc, by = c("subjid", "ds", "time"), all = TRUE)

exc.list <- exc.list %>%
  mutate(mot.exc = 1) 

## Final Numbers - 43 FS exclusion based on Euler Number - 25th percentile - 1.5*IQR (117) + failed Visual QC (left 43)
##               - 289  CONN exclusion based on >25% invalid scans + 1 ID with 6 vol  
## Total of 304 scans 

write_csv(exc.list, '/data/motion_exc_list.csv')

```


## Load Data
```{r}

exc.list <- read_csv('/data/motion_exc_list.csv')

exc.list <- exc.list %>%
  select(subjid, time, mot.exc)

df_ids <- read_csv('/data/df_included.csv')

df_ids <- merge(df_ids, exc.list, by = c("subjid", "time"), all.x = TRUE)

df_ids <- df_ids %>%
  select(subjid, Cohort, time, ScanAge, sex, Dataset, mot.exc) %>%
  unique(.)

```


```{r}

df <- read_csv("/data/dfe_har.csv")

df_fil <- merge(df, df_ids, by = c("subjid", "ScanAge", "time", "sex"), all.x = TRUE)

df_fil <- df_fil %>%
  filter(is.na(mot.exc))

table(df_fil$Dataset)
table(df_fil$test)

```

## GPBOOST PREP
```{r}

dff <- transform(df_fil, id = as.numeric(factor(subjid)))

id.key <- dff %>%
  select(subjid, id) %>%
  unique()

```

## Stratify by Phase 
```{r}

dff1 <- dff %>%
  filter(time < 4 | time == 6)

dff2 <- dff %>%
  filter(time >=3 & time < 6)

fivenum(dff1$ScanAge)
fivenum(dff2$ScanAge)

```

## Stratify by Sex
### Phase 1 (up to 8YO)
```{r}

dff1.m <- dff1 %>%
  filter(sex == "Male") %>%
  arrange(subjid, ScanAge)

test_dat1.m <- dff1.m %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train1.m <- dff1.m %>%
  filter(is.na(test))

dff1.f <- dff1 %>%
  filter(sex == "Female") %>%
  arrange(subjid, ScanAge)

test_dat1.f <- dff1.f %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train1.f <- dff1.f %>%
  filter(is.na(test))

```

### Phase 2 (up to 7 to 13YO)
```{r}

dff2.m <- dff2 %>%
  filter(sex == "Male") %>%
  arrange(subjid, ScanAge)

test_dat2.m <- dff2.m %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train2.m <- dff2.m %>%
  filter(is.na(test))

dff2.f <- dff2 %>%
  filter(sex == "Female") %>%
  arrange(subjid, ScanAge)

test_dat2.f <- dff2.f %>%
  filter(test == 1) %>%
  select(subjid, id, ScanAge, time, batch, ds)

train2.f <- dff2.f %>%
  filter(is.na(test))

```

Create Folds for internal validation
**FOLDS REPEATED - Males Phase 1**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

rand.seed <- sample(1:1000,10)
folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:336, 336) 

  k.folds <- groupKFold(group = train1.m[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.m1 <- flatten(folds.out)

```

**FOLDS REPEATED - Males Phase 2**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:404, 404) 

  k.folds <- groupKFold(group = train2.m[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.m2 <- flatten(folds.out)

```

**FOLDS REPEATED - Females Phase 1**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:396, 396) 

  k.folds <- groupKFold(group = train1.f[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.f1 <- flatten(folds.out)

```

**FOLDS REPEATED - Females Phase 2**
```{r}
# Partition training data into inner training data and validation data making sure same IDs are in the same group

folds.out <- list()

for (i in 1:5) {
  set.seed(rand.seed[i])
  row_number <- matrix(1:467, 467) 

  k.folds <- groupKFold(group = train2.f[,1], k = 5)

  k.folds2 <- k.folds$Fold2
  k.folds3 <- row_number[-k.folds2,]

  k.folds4 <- k.folds$Fold1
  k.folds5 <- row_number[-k.folds4,]

  k.folds6 <- k.folds$Fold3
  k.folds7 <- row_number[-k.folds6,]

  k.folds8 <- k.folds$Fold4
  k.folds9 <- row_number[-k.folds8,]

  k.folds10 <- k.folds$Fold5
  k.folds11 <- row_number[-k.folds10,]

  folds.out[[i]] <- list(k.folds3, k.folds5, k.folds7, k.folds9, k.folds11)
}

folds.f2 <- flatten(folds.out)

```

```{r}

# Specify parameter grid, gp_model, and gpb.Dataset
param_grid <- list("learning_rate" = c(1,0.1,0.01), "max_depth" = c(1,2,3,5,10,15),"min_data_in_leaf" = c(5,10,50,100), "lambda_l2" = c(0,1,10,25,50))
other_params <- list(num_leaves = 2^10)

```

## A2 Freesurfer Thickness + Subcort + 17 FC Integration
### Males 1
```{r}
# convert data into matrix

data_train <- dff1.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff1.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 1)
nrounds <- 478
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.m1 <- gpb.out
mod.a2.m1 <- shap.plot.summary.wrap1(a2.out.m1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.m1

```

#### Values
```{r}
shap.a2.m1 <- shap.values(a2.out.m1, X_train = data_train[,pred_vars])
shap.a2.m1 <- as.data.frame(shap.a2.m1$mean_shap_score)
shap.a2.m1 <- shap.a2.m1 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m1$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m1, '/figs/supp/motion/shap.a2.m1_mot.csv')

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.m1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.m$gpb_pred_a2 <- pred[["response_mean"]]


```


### Males 2
```{r}
# convert data into matrix

data_train <- dff2.m %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff2.m %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])

```


```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.m2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.1, max_depth = 2, num_leaves = 2^10, min_data_in_leaf = 5, lambda_l2 = 1)
nrounds <- 145
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.m2 <- gpb.out
mod.a2.m2 <- shap.plot.summary.wrap1(a2.out.m2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.m2

```

#### Values
```{r}

shap.a2.m2 <- shap.values(a2.out.m2, X_train = data_train[,pred_vars])
shap.a2.m2 <- as.data.frame(shap.a2.m2$mean_shap_score)
shap.a2.m2 <- shap.a2.m2 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.m2$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.m2, '/figs/supp/motion/shap.a2.m2_mot.csv')

```


### Predict Age in Test 
```{r}

pred <- predict(a2.out.m2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.m$gpb_pred_a2 <- pred[["response_mean"]]

```


### Females 1
```{r}
# convert data into matrix

data_train <- dff1.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff1.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f1,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 1, num_leaves = 2^10, min_data_in_leaf = 10, lambda_l2 = 1)
nrounds <- 1628
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.f1 <- gpb.out
mod.a2.f1 <- shap.plot.summary.wrap1(a2.out.f1, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.f1

```

#### Values
```{r}

shap.a2.f1 <- shap.values(a2.out.f1, X_train = data_train[,pred_vars])
shap.a2.f1 <- as.data.frame(shap.a2.f1$mean_shap_score)
shap.a2.f1 <- shap.a2.f1 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f1$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f1, '/figs/supp/motion/shap.a2.f1_mot.csv')

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.f1, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat1.f$gpb_pred_a2 <- pred[["response_mean"]]

```


### Females 2
```{r}
# convert data into matrix

data_train <- dff2.f %>%
  filter(is.na(test)) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

data_test <- dff2.f %>%
  filter(test == 1) %>%
  select(id, ScanAge, matches("thickness"), matches("left|right"), starts_with("Int"), modularity.combat) %>%
  as.matrix()

# Define fixed effects predictor variables
pred_vars <- colnames(data_train)[3:221]

gp_model <- GPModel(group_data = data_train[,"id"], likelihood = "gaussian")
data_bst <- gpb.Dataset(data = data_train[,pred_vars], label = data_train[,"ScanAge"])


```

```{r}

# Find optimal tuning parameters
opt_params <- gpb.grid.search.tune.parameters(
  param_grid = param_grid, 
  params = other_params,
  num_try_random = NULL, 
  folds = folds.f2,
  data = data_bst, 
  gp_model = gp_model,
  nrounds = 2000, 
  early_stopping_rounds = 10,
  verbose_eval = 1, metric = c("rmse"))

opt_params

```

```{r}

params <- list(learning_rate = 0.01, max_depth = 3, num_leaves = 2^10, min_data_in_leaf = 50, lambda_l2 = 0)
nrounds <- 1001
gpb.out <- gpb.train(data = data_bst, gp_model = gp_model, 
                   nrounds = nrounds, params = params, verbose = 1)
summary(gp_model)

```

### SHAP
#### Plot
```{r}

a2.out.f2 <- gpb.out
mod.a2.f2 <- shap.plot.summary.wrap1(a2.out.f2, X = data_train[,pred_vars], top_n=30) +  ggtitle("SHAP values")

mod.a2.f2

```

#### Values
```{r}

shap.a2.f2 <- shap.values(a2.out.f2, X_train = data_train[,pred_vars])
shap.a2.f2 <- as.data.frame(shap.a2.f2$mean_shap_score)
shap.a2.f2 <- shap.a2.f2 %>%
  mutate(region = row.names(.)) %>%
  rename(mean_shap_score = `shap.a2.f2$mean_shap_score`) %>%
  mutate(modality = ifelse(
    str_detect(region, "thickness"), "S-CT", ifelse(
    str_detect(region, "left|right"), "S-Volume", "F-Integration"  
    ))) %>%
  select(region, modality, mean_shap_score)

write_csv(shap.a2.f2, '/figs/supp/motion/shap.a2.f2_mot.csv')

```

### Predict Age in Test 
```{r}

pred <- predict(a2.out.f2, 
                data = data_test[,pred_vars],
                group_data_pred = data_test[,"id"], 
                predict_var = FALSE, 
                pred_latent = FALSE)

test_dat2.f$gpb_pred_a2 <- pred[["response_mean"]]

```


### Write Test Data
```{r}

test_dat1.f <- test_dat1.f %>%
  mutate(sex = "Female") %>%
  mutate(phase = "Early-Childhood")

test_dat2.f <- test_dat2.f %>%
  mutate(sex = "Female") %>%
  mutate(phase = "Late-Childhood")

test_dat1.m <- test_dat1.m %>%
  mutate(sex = "Male") %>%
  mutate(phase = "Early-Childhood")

test_dat2.m <- test_dat2.m %>%
  mutate(sex = "Male") %>%
  mutate(phase = "Late-Childhood")

test_dat_mot <- rbind(test_dat1.f, test_dat2.f, test_dat1.m, test_dat2.m)

test_dat_mot <- test_dat_mot %>%
  rename(gpb_pred_a2_mot = gpb_pred_a2)

write_csv(test_dat_mot, '/figs/supp/motion/gpb_pred_a2_mot.csv')

```

